### 2017-03-24 paper/oopsla17-submission/evaluation-accuracy.tex
minor

\paragraph{Our Classifiers}
We evaluate five classifiers, each trained on the full set of 276
features: 44 local syntactic features, 176 contextual syntactic
features, 55 typing features, and a single expression size feature.
%
\ES{should explain the make-up of these groups}
%
We preemptively discard expressions that are not part of the minimal
type error slice, we will explain the rationale for this in
\autoref{sec:feature-utility}.
%
Our classifiers are:
%
\begin{enumerate}
\item A logistic regression trained with a learning rate
  $\alpha = 0.001$, an L2 regularization rate $\lambda = 0.001$, and a
  mini-batch size of 200.
\item A decision tree \ES{HUMA: hyperparams?}.
\item A random forest with 30 estimators \ES{HUMA: hyperparams?}.
\item Two multi-layer perceptrons, both trained with $\alpha = 0.001$,
  $\lambda = 0.001$, and a mini-batch size of 200. The first MLP
  contains a single hidden layer of 10 neurons, and the second contains
  a hidden layer of 500 neurons. This allows us to investigate how well
  the MLP can \emph{compress} its model.
\end{enumerate}
%
All classifiers were trained for 20 epochs on one dataset
--- \ie they were shown each program 20 times ---
before being evaluated on the other.

@@

Interestingly there is little variation in accuracy between classifiers
with the exception of the \linear model, they all achieve around 70\%
Top-1 accuracy and around 90\% Top-3 accuracy.
%
In particular, the \hiddenT only loses around 2\% accuracy compared to
the \hiddenFH, which suggests that it can substantially compress the
model.
%
We also note that our classifiers consistently perform better when
trained on the \FALL programs and tested on the \SPRING programs than
vice versa, they appear to generalize better from the \FALL data.

>>>>

\paragraph{Our Classifiers}
We evaluate five classifiers, each trained on the full set of 276
features: 44 local syntactic features, 176 contextual syntactic
features, 55 typing features, and a single expression size feature.
%
\ES{should explain the make-up of these groups}
%
We preemptively discard expressions that are not part of the minimal
type error slice, we will explain the rationale for this in
\autoref{sec:feature-utility}.
%
Our classifiers are:
%
\begin{enumerate}
\item A logistic regression trained with a learning rate
  $\alpha = 0.001$, an L2 regularization rate $\lambda = 0.001$, and a
  mini-batch size of 200.
\item A decision tree trained with the \ES{HUMA?} algorithm and \ES{HUMA: hyperparams?}.
\item A random forest trained with the \ES{HUMA?} algorithm and 30 estimators \ES{HUMA: hyperparams?}.
\item Two multi-layer perceptrons, both trained with $\alpha = 0.001$,
  $\lambda = 0.001$, and a mini-batch size of 200. The first MLP
  contains a single hidden layer of 10 neurons, and the second contains
  a hidden layer of 500 neurons. This allows us to investigate how well
  the MLP can \emph{compress} its model.
\end{enumerate}
%
All classifiers were trained for 20 epochs on one dataset
--- \ie they were shown each program 20 times ---
before being evaluated on the other.

@@

Surprisingly, there is little variation in accuracy between classifiers
with the exception of the \linear model, they all achieve around 70\%
Top-1 accuracy and around 90\% Top-3 accuracy.
%
This would appear to suggest that the model they learn is relatively
simple.
%
In particular, notice that although the \hiddenT has $50\times$ \emph{fewer}
hidden features than the \hiddenFH, it only loses around 2\% accuracy.
% In particular, notice that the \hiddenT only loses around 2\% accuracy
% compared to the \hiddenFH,
%
We also note that our classifiers consistently perform better when
trained on the \FALL programs and tested on the \SPRING programs than
vice versa, they appear to generalize better from the \FALL data.
